Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2025-01-03 ms.qmd
Few corrections. Still deciding on what to do with sim fig

```{r, fig-sim}
#| label: fig-sim
#| fig-align: center
#| fig-cap: "Simulated performance curves for *n* = 40 individuals in four hypothetical scenerios with varying performance breadth ($\\sigma$), optima ($\\delta$) and skewness ($\\alpha$). Individual performance curves are different colours. $lnCVR_{Q_{10}}$ is calculated as the log transformed ratio of the coefficient of variance (CV) in performance at the higher temperature divided by the CV in performance at that temperature at each point along the curve. $lnVR_{Q_{10}}$ is calculated as the log transformed ratio of the standard deviation in performance at the higher temperature divided by the standard deviation in performance at that temperature. The dashed red line indicates the higher temperature (28°C) and the dashed blue line indicates the lower temperature (18°C). Note that the mean ($\\mu$) and standard deviation ($\\sigma$) of physiological rates are shown for each temperature. In all simulations, $\\delta$ = 35, $\\sigma$ = 9 and $\\alpha$ = -15, while between individual variation for $\\sigma_{\\delta}$ = 1,  $\\sigma_{\\sigma}$ = 0.5 and $\\sigma_{\\alpha}$ = 0.5."

>>>>

```{r, fig-sim}
#| label: fig-sim
#| fig-align: center
#| fig-cap: "Simulated performance curves for *n* = 40 individuals in four hypothetical scenarios with varying performance breadth ($\\sigma$), optima ($\\delta$) and skewness ($\\alpha$). Individual performance curves are different colours. $lnCVR_{Q_{10}}$ is calculated as the log transformed ratio of the coefficient of variance (CV) in performance at the higher temperature divided by the CV in performance at that temperature at each point along the curve. $lnVR_{Q_{10}}$ is calculated as the log transformed ratio of the standard deviation in performance at the higher temperature divided by the standard deviation in performance at that temperature. The dashed red line indicates the higher temperature (28°C) and the dashed blue line indicates the lower temperature (18°C). Note that the mean ($\\mu$) and standard deviation ($\\sigma$) of physiological rates are shown for each temperature. In all simulations, $\\delta$ = 35, $\\sigma$ = 9 and $\\alpha$ = -15, while between individual variation for $\\sigma_{\\delta}$ = 1,  $\\sigma_{\\sigma}$ = 0.5 and $\\sigma_{\\alpha}$ = 0.5."
